Insert the article title here

### 2018-05-14 Writeup/sup_mat.tex
shrinking methods in main text

@@

\begin{table*}
\centering
\small
\begin{tabular}{c|c|r|r|r}
 		&	& $1<n$	& $2 \leq n \leq 5$ & $2 \leq n \leq 3$\\
\hline
\multirow{3}{*}{easy} 
& central		& 3931 	& 3689	& \\
& homogeneous 	& 12452	& 8312 	&\\
& heterogeneous & 5955	& 3241 	&\\
\hline
\multirow{3}{*}{hard} 
& central		& 3804 	& 2439	& \\
& homogeneous 	& 8781	& 3188	&	\\
& heterogeneous & 29912	& 5294	&\\
\hline
\multirow{3}{*}{absent} 
& central		& 16885 & 8303	& \\
& homogeneous 	& 41356	& 12576	&\\
& heterogeneous & 192348& 5763	&\\
\hline
\end{tabular}
\caption{Number of fixations recorded for each condition.}
\label{tab:num_fix}
\end{table*}

>>>>

\section{Paradigm Details}

\subsection{Split-half}

The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes [Or identical to the task described in Experiment 1 of Irons \& Leber, in press by then hopefully].

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors changes colours from trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

A white digit appeared inside each square. Two targets - a red square and a blue square each with a digit between 2 and 5 - were embedded in every search display. The two target digits were always different, to enable us to distinguish the chosen target. The remaining red, blue and variable squares all contained digits between 6-9. Green squares could contain any digit between 2-9. The location of the targets and distractor within the search display were randomized on each trial.

Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one. A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made. Participant responded by pressing a key that corresponded to the digit inside the target (\texttt{V}, \texttt{B}, \texttt{N} and \texttt{M} keys corresponding to 2, 3, 4 and 5 respectively). Participants completed 10 practice trials, followed by 3 blocks of 96 trials. Each block started on a red plateau.

The foraging task was based on \cite{kristjansson2014} and \cite{johannesson2016}. Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).

In the feature foraging task, search displays contained 80 small circles (size), 20 red (RGB: 180, 0, 0), 20 green (RGB: 20, 100, 40), 20 blue (RGB: 0, 0, 220) and 20 yellow (RGB: 200, 150, 0), presented against a black background. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other). The location of item colours to grid locations was completely randomized. 
For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun. Participants completed 1 practice trial and 20 full-completed experimental trials.

In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search). Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.

@@

\begin{table*}
\centering
\small
\begin{tabular}{c|c|r|r|r}
 		&	& $1<n$	& $2 \leq n \leq 5$ & $2 \leq n \leq 3$\\
\hline
\multirow{3}{*}{easy} 
& central		& 3931 	& 3689	& \\
& homogeneous 	& 12452	& 8312 	&\\
& heterogeneous & 5955	& 3241 	&\\
\hline
\multirow{3}{*}{hard} 
& central		& 3804 	& 2439	& \\
& homogeneous 	& 8781	& 3188	&	\\
& heterogeneous & 29912	& 5294	&\\
\hline
\multirow{3}{*}{absent} 
& central		& 16885 & 8303	& \\
& homogeneous 	& 41356	& 12576	&\\
& heterogeneous & 192348& 5763	&\\
\hline

\end{tabular}
\caption{Number of fixations recorded for each condition.}
\label{tab:num_fix}
\end{table*}

### 2018-05-14 writeup/manuscript.tex
shrinking methods in main text

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial.

The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000 Hz.
This paradigm was carried out twice to give us an estimate of how consistent participants are in their search strategy over time. The two sessions were identical.

@@

The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes [Or identical to the task described in Experiment 1 of Irons \& Leber, in press by then hopefully].

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors changes colours from trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

@@

Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one. A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made. Participant responded by pressing a key that corresponded to the digit inside the target (\texttt{V}, \texttt{B}, \texttt{N} and \texttt{M} keys corresponding to 2, 3, 4 and 5 respectively). Participants completed 10 practice trials, followed by 3 blocks of 96 trials. Each block started on a red plateau.

@@

In the feature foraging task, search displays contained 80 small circles (size), 20 red (RGB: 180, 0, 0), 20 green (RGB: 20, 100, 40), 20 blue (RGB: 0, 0, 220) and 20 yellow (RGB: 200, 150, 0), presented against a black background. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other). The location of item colours to grid locations was completely randomized. 
For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun. Participants completed 1 practice trial and 20 full-completed experimental trials.

@@

%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search). Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well. 
\subsection{Planned Analysis}

>>>>

A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

This paradigm was carried out twice to give us an estimate of how consistent participants are in their search strategy over time. The two sessions were identical.

@@

The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes.

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one.

@@

In the feature foraging task, search displays contained 80 small circles (size), 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized.

For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun.

@@

%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search). Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.

\subsection{Planned Analysis}
